\documentclass{beamer}

\usepackage{beamerthemetuw}
%\usepackage{enumitem}
\setbeamercovered{transparent}


\title{Formally Verifying Rust}
\subtitle{Making sure your code works}
\author{Mark Chimes}
\date{\today}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{Outline}
\tableofcontents
\end{frame}

\section{Rust}
\begin{frame}{Overview}
\begin{block}{What will we do?}
\begin{itemize} 
	\item Introduce Rust
	\item Intrduce Formal verification
	\item Motivate Rust with formal verification
	\item Expand on Rust
	\item Expand on Formal verification
	\item Expand on motivation
\end{itemize}
\end{block}
\end{frame}


\section{Rust Intro}
\begin{frame}{Rust}
\begin{block}{What is Rust?}
\end{block}
\end{frame}

\begin{frame}{Rust}
\begin{block}{What is Rust?}
Rust is a programming language
\end{block}
\end{frame}

\begin{frame}{Formal Verification}
\begin{block}{What is Formal Verification?}
\end{block}
\end{frame}

\begin{frame}{Rust}
\begin{block}{What is Rust? (for real this time)}
\begin{itemize}
	\item Rust is a \textbf{systems} programming language
	\begin{itemize}
		\item low-level control
		\item fast / efficient
	\end{itemize}
	\item strongly-typed
	\item slower initial devlopment, faster maintainence
	\item modern
\end{itemize}
\end{block}
\begin{block}{Special Sauce} 
Memory safety guarantees without garbage collection
\end{block}
\end{frame}

\section{Formal Verification Intro}
\begin{frame}{Formal Verification}
\begin{block}{What is Formal Verification?}
\begin{itemize} 
\item Logically ``prove" correctness of a program
\item Usually labour-intensive process
\end{itemize} 
\end{block}
\end{frame}


\section{Combination}
\begin{frame}{Why?}
Why? 
\end{frame}

\section{Diving Deeper into Rust}
\begin{frame}{Why?}
Why? 
\end{frame}


\end{document}
